---
title: "DEMINOVA LAB"
subtitle: "Meeting Report: Chile Case ⅠⅠⅠ"
author: David & Natalia
institute: Department of Global Studies
date: today
date-format: "dddd, [the] D[<sup style='font-size:40%;font-style:italic;'></sup>] [of] MMMM, YYYY"
embed-resources: false
format: aarhus-revealjs
---

```{r}
#| include: false


sysfonts::font_add_google("Alegreya Sans", "Alegreya Sans", regular.wt = 300)
showtext::showtext_auto()

if (!require("pacman")) install.packages("pacman")
pacman::p_load(
  tidyverse, lubridate, dplyr, purrr, tibble,     # Tidyverse
  tidyr, tidyr, data.table, kableExtra,           # Data Pre-processing
  parallel, future, furrr, future.apply,          # Parallel Computing
  doParallel, foreach, doFuture, dplyr,
  ggplot2, ggpubr, ggrepel, wesanderson, ggraph,  # Visualization Toolkit
  cowplot, lattice, igraph, ggforce, tidygraph,
  tidyverse, lubridate, dplyr, purrr, tibble,     # Tidyverse Toolkit  
  quanteda, tmcn, austin, udpipe, textrank,       # NLP toolkit
  emIRT                                           # Generalized Wordfish
)

```

```{r}
#| include: false

# read the files
load("../deminova-data/cooc_tokened_event1.RData")
load("../deminova-data/cooc_tokened_event2.RData")
load("../deminova-data/cooc_tokened_event3.RData")
load("../deminova-data/cooc_tokened_event4.RData")
load("../deminova-data/cooc_tokened_event5.RData")

colnames(cooc_tokened_event1)[3] <- "Co-Occurrence Windows"
colnames(cooc_tokened_event2)[3] <- "Co-Occurrence Windows"
colnames(cooc_tokened_event3)[3] <- "Co-Occurrence Windows"
colnames(cooc_tokened_event4)[3] <- "Co-Occurrence Windows"
colnames(cooc_tokened_event5)[3] <- "Co-Occurrence Windows"


edge_colour_set <- c("#d4db87", "grey", "#29000f", "#29000f", "#4b0909")
color_palette_set <- c("#DBB887", "#1380A1", "#588300",  "#e69138")
```


```{r}
#| include: false
demo_words <- c("democracia", 
                "demócrata",
                "demócratas",
                "democrática", 
                "democráticas",
                "democrático",
                "democráticos",
                "democráticamente",
                "democratización",
                "democratizaciones",
                "democratizador",
                "democratizadora",
                "democratizar",
                "democratizada",
                "democratizadas",
                "democratizado",
                "democratizados")

cooc_event1 <- cooc_tokened_event1[cooc_tokened_event1$term1 %in% demo_words |
                                     cooc_tokened_event1$term2  %in% demo_words,]


cooc_event2 <- cooc_tokened_event2[cooc_tokened_event2$term1 %in% demo_words |
                                     cooc_tokened_event2$term2  %in% demo_words,]



cooc_event3 <- cooc_tokened_event3[cooc_tokened_event3$term1 %in% demo_words |
                                     cooc_tokened_event3$term2  %in% demo_words,]


cooc_event4 <- cooc_tokened_event4[cooc_tokened_event4$term1 %in% demo_words |
                                     cooc_tokened_event4$term2  %in% demo_words,]

cooc_event5 <- cooc_tokened_event5[cooc_tokened_event5$term1 %in% demo_words |
                                     cooc_tokened_event5$term2  %in% demo_words,]

```


```{r}
#| include: false
# remove the stopword in the list
stopwordlist <- c("RT", "Rosalía", "via", "s", "es")
cooc_event1 <- cooc_event1[!cooc_event1$term1 %in% stopwordlist | cooc_event1$term2 %in% stopwordlist, ]

cooc_event2 <- cooc_event2[!cooc_event2$term1 %in% stopwordlist | cooc_event2$term2 %in% stopwordlist, ]

cooc_event3 <- cooc_event3[!cooc_event3$term1 %in% stopwordlist | cooc_event3$term2 %in% stopwordlist, ]
```


```{r}
#| include: false
# collapse date 1018
cooc_event1[cooc_event1$term1 %in% c("pais", "país"),]$term1 <-"pais"
cooc_event1[cooc_event1$term2 %in% c("pais", "país"), ]$term2 <-"pais"
cooc_event1[cooc_event1$term1 %in% c("r3ch4z0", "rechazo", "r3ch4zo"), ]$term1 <- "rechazo" 
cooc_event1[cooc_event1$term2 %in% c("r3ch4z0", "rechazo", "r3ch4zo"), ]$term2 <- "rechazo"
# ---------------- #
cooc_event1[cooc_event1$term1 %in% c("histó", "historico", "histórico"), ]$term1 <-"histó" 
cooc_event1[cooc_event1$term2 %in% c("histó", "historico", "histórico"), ]$term2 <-"histó"
# ---------------- #
  
cooc_event1[cooc_event1$term1 %in% c("chilenos", "chilenas", "chilen@s"), ]$term1 <- "chilenos" 
cooc_event1[cooc_event1$term2 %in% c("chilenos", "chilenas", "chilen@s"), ]$term2  <- "chilenos" 
cooc_event1[cooc_event1$term1 %in% c("sera", "será"), ]$term1 <- "sera"
cooc_event1[cooc_event1$term2 %in% c("sera", "será"), ]$term2 <- "sera"
# ---------------- #
    
cooc_event1[cooc_event1$term1 %in% c("subsidiario", "subsidiaria", "subsidiariedad"), ]$term1 <- "subsidiario"
cooc_event1[cooc_event1$term2 %in% c("subsidiario", "subsidiaria", "subsidiariedad"), ]$term2 <- "subsidiario"
# ---------------- #


cooc_event1[cooc_event1$term1 %in% c("participativo", "participativa"), ]$term1<- "participativo"  
cooc_event1[cooc_event1$term2 %in% c("participativo", "participativa"), ]$term2 <- "participativo" 

# ---------------- #

cooc_event1[cooc_event1$term1 %in% c("água", "agua"), ]$term1 <-"agua"
cooc_event1[cooc_event1$term2 %in% c("água", "agua"), ]$term2 <- "agua"
# ---------------- #
  
cooc_event1[cooc_event1$term1 %in% c("nuevo", "nueva"), ]$term1 <- "nuevo"
cooc_event1[cooc_event1$term2 %in% c("nuevo", "nueva"), ]$term2 <- "nuevo"
# ---------------- #
  
cooc_event1[cooc_event1$term1 %in% c("demócrata", "demócratas"), ]$term1 <- "demócratas"
cooc_event1[cooc_event1$term2 %in% c("demócrata", "demócratas"), ]$term2 <- "demócratas"
# ---------------- #
cooc_event1[cooc_event1$term1 %in% c("democrática", "democráticas", "democrático", "democráticos"), ]$term1 <- "democrática"
cooc_event1[cooc_event1$term2 %in% c("democrática", "democráticas", "democrático", "democráticos"), ]$term2 <- "democrática"
# ---------------- #

cooc_event1[cooc_event1$term1 %in% c("democratización", "democratizaciones"), ]$term1 <- "democratización"
cooc_event1[cooc_event1$term2 %in% c("democratización", "democratizaciones"), ]$term2 <- "democratización"
# ---------------- #
  
cooc_event1[cooc_event1$term1 %in% c("democratizador", "democratizadora"), ]$term1 <- "democratizador"
cooc_event1[cooc_event1$term2 %in% c("democratizador", "democratizadora"), ]$term2 <- "democratizador"
# ---------------- #

cooc_event1[cooc_event1$term1 %in% c("democratizada", "democratizadas", "democratizado", "democratizados"), ]$term1 <- "democratizada"
cooc_event1[cooc_event1$term2 %in% c("democratizada", "democratizadas", "democratizado", "democratizados"), ]$term2 <- "democratizada"

# ---------------- #

cooc_event1[cooc_event1$term1 %in% c("Derecho", "derecho", "Derechos", "derechos"), ]$term1 <- "Derecho"
cooc_event1[cooc_event1$term2 %in% c("Derecho", "derecho", "Derechos", "derechos"), ]$term2 <- "Derecho"
# ---------------- #

cooc_event1[cooc_event1$term1 %in% c("Derecha", "Derechas", "derecha", "derechas"), ]$term1 <- "Derecha"
cooc_event1[cooc_event1$term2 %in% c("Derecha", "Derechas", "derecha", "derechas"), ]$term2 <- "Derecha"
# ---------------- #

cooc_event1[cooc_event1$term1 %in% c("#Apruebo", "Apruebo", "#apruebo", "apruebo"), ]$term1 <- "Apruebo"
cooc_event1[cooc_event1$term2 %in% c("#Apruebo", "Apruebo", "#apruebo", "apruebo"), ]$term2 <- "Apruebo"
# ---------------- #


cooc_event1[cooc_event1$term1 %in% c("AsambleaConstiyente", "#AsambleaConstiyente", "#AsambleaConstituyente", "#AsambleaConstituyente", "asambleaconstituyente", "#asambleaconstituyente"), ]$term1 <- "AsambleaConstiyente"
cooc_event1[cooc_event1$term2 %in% c("AsambleaConstiyente", "#AsambleaConstiyente", "#AsambleaConstituyente", "#AsambleaConstituyente", "asambleaconstituyente", "#asambleaconstituyente"), ]$term2 <- "AsambleaConstiyente"

```


```{r}
#| include: false
# collapse date 1025
cooc_event2[cooc_event2$term1 %in% c("pais", "país"),  "term1" ]$term1 <-"pais"
cooc_event2[cooc_event2$term2 %in% c("pais", "país"), "term2" ]$term2 <-"pais"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("r3ch4z0", "rechazo", "r3ch4zo"), ]$term1 <- "rechazo" 
cooc_event2[cooc_event2$term2 %in% c("r3ch4z0", "rechazo", "r3ch4zo"), ]$term2 <- "rechazo"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("histó", "historico", "histórico"), ]$term1 <-"histó"
cooc_event2[cooc_event2$term2 %in% c("histó", "historico", "histórico"), ]$term2 <-"histó"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("chilenos", "chilenas", "chilen@s"), ]$term1 <- "chilenos" 
cooc_event2[cooc_event2$term2 %in%  c("chilenos", "chilenas", "chilen@s"), ]$term2 <- "chilenos" 
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("sera", "será"), ]$term1 <- "sera"
cooc_event2[cooc_event2$term2 %in% c("sera", "será"), ]$term2 <- "sera"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("subsidiario", "subsidiaria", "subsidiariedad"), ]$term1 <- "subsidiario"
cooc_event2[cooc_event2$term2 %in% c("subsidiario", "subsidiaria", "subsidiariedad"), ]$term2 <- "subsidiario"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("participativo", "participativa"), ]$term1 <- "participativo" 
cooc_event2[cooc_event2$term2 %in% c("participativo", "participativa"), ]$term2 <- "participativo" 
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("água", "agua"), ]$term1 <- "agua"
cooc_event2[cooc_event2$term2 %in% c("água", "agua"), ]$term2 <- "agua" 
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("nuevo", "nueva"), ]$term1 <- "nuevo" 
cooc_event2[cooc_event2$term2 %in% c("nuevo", "nueva"), ]$term2 <- "nuevo"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("demócrata", "demócratas"), ]$term1 <- "demócratas"
cooc_event2[cooc_event2$term2 %in% c("demócrata", "demócratas"), ]$term2 <- "demócratas"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("democrática", "democráticas", "democrático", "democráticos"), ]$term1 <- "democrática"
cooc_event2[cooc_event2$term2 %in% c("democrática", "democráticas", "democrático", "democráticos"), ]$term2 <- "democrática"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("democratización", "democratizaciones"), ]$term1 <- "democratización"
cooc_event2[cooc_event2$term2 %in% c("democratización", "democratizaciones"), ]$term2 <- "democratización"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("democratizador", "democratizadora"), ]$term1 <- "democratizador"
cooc_event2[cooc_event2$term2 %in% c("democratizador", "democratizadora"), ]$term2 <- "democratizador"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("democratizada", "democratizadas", "democratizado", "democratizados"), ]$term1 <- "democratizada"
cooc_event2[cooc_event2$term2 %in% c("democratizada", "democratizadas", "democratizado", "democratizados"), ]$term2 <- "democratizada"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("Derecho", "derecho", "Derechos", "derechos"), ]$term1 <- "Derecho"
cooc_event2[cooc_event2$term2 %in% c("Derecho", "derecho", "Derechos", "derechos"), ]$term2 <- "Derecho"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("Derecha", "Derechas", "derecha", "derechas"), ]$term1 <- "Derecha"
cooc_event2[cooc_event2$term2 %in% c("Derecha", "Derechas", "derecha", "derechas"), ]$term2 <- "Derecha"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("#Apruebo", "Apruebo", "#apruebo", "apruebo"), ]$term1 <- "Apruebo"
cooc_event2[cooc_event2$term2 %in% c("#Apruebo", "Apruebo", "#apruebo", "apruebo"), ]$term2 <- "Apruebo"
# ---------------- #
cooc_event2[cooc_event2$term1 %in% c("AsambleaConstiyente", "#AsambleaConstiyente", "#AsambleaConstituyente", "#AsambleaConstituyente", "asambleaconstituyente", "#asambleaconstituyente"), ]$term1 <- "AsambleaConstiyente"
cooc_event2[cooc_event2$term2 %in% c("AsambleaConstiyente", "#AsambleaConstiyente", "#AsambleaConstituyente", "#AsambleaConstituyente", "asambleaconstituyente", "#asambleaconstituyente"), ]$term2 <- "AsambleaConstiyente"
```


```{r}
#| include: false
# collapse date 1115
cooc_event3[cooc_event3$term1 %in% c("pais", "país"),  "term1" ]$term1 <-"pais"
cooc_event3[cooc_event3$term2 %in% c("pais", "país"), "term2" ]$term2 <-"pais"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("r3ch4z0", "rechazo", "r3ch4zo"), ]$term1 <- "rechazo" 
cooc_event3[cooc_event3$term2 %in% c("r3ch4z0", "rechazo", "r3ch4zo"), ]$term2 <- "rechazo"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("histó", "historico", "histórico"), ]$term1 <-"histó"
cooc_event3[cooc_event3$term2 %in% c("histó", "historico", "histórico"), ]$term2 <-"histó"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("chilenos", "chilenas", "chilen@s"), ]$term1 <- "chilenos" 
cooc_event3[cooc_event3$term2 %in%  c("chilenos", "chilenas", "chilen@s"), ]$term2 <- "chilenos" 
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("sera", "será"), ]$term1 <- "sera"
cooc_event3[cooc_event3$term2 %in% c("sera", "será"), ]$term2 <- "sera"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("subsidiario", "subsidiaria", "subsidiariedad"), ]$term1 <- "subsidiario"
cooc_event3[cooc_event3$term2 %in% c("subsidiario", "subsidiaria", "subsidiariedad"), ]$term2 <- "subsidiario"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("participativo", "participativa"), ]$term1 <- "participativo" 
cooc_event3[cooc_event3$term2 %in% c("participativo", "participativa"), ]$term2 <- "participativo" 
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("água", "agua"), ]$term1 <- "agua"
cooc_event3[cooc_event3$term2 %in% c("água", "agua"), ]$term2 <- "agua" 
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("nuevo", "nueva"), ]$term1 <- "nuevo" 
cooc_event3[cooc_event3$term2 %in% c("nuevo", "nueva"), ]$term2 <- "nuevo"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("demócrata", "demócratas"), ]$term1 <- "demócratas"
cooc_event3[cooc_event3$term2 %in% c("demócrata", "demócratas"), ]$term2 <- "demócratas"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("democrática", "democráticas", "democrático", "democráticos"), ]$term1 <- "democrática"
cooc_event3[cooc_event3$term2 %in% c("democrática", "democráticas", "democrático", "democráticos"), ]$term2 <- "democrática"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("democratización", "democratizaciones"), ]$term1 <- "democratización"
cooc_event3[cooc_event3$term2 %in% c("democratización", "democratizaciones"), ]$term2 <- "democratización"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("democratizador", "democratizadora"), ]$term1 <- "democratizador"
cooc_event3[cooc_event3$term2 %in% c("democratizador", "democratizadora"), ]$term2 <- "democratizador"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("democratizada", "democratizadas", "democratizado", "democratizados"), ]$term1 <- "democratizada"
cooc_event3[cooc_event3$term2 %in% c("democratizada", "democratizadas", "democratizado", "democratizados"), ]$term2 <- "democratizada"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("Derecho", "derecho", "Derechos", "derechos"), ]$term1 <- "Derecho"
cooc_event3[cooc_event3$term2 %in% c("Derecho", "derecho", "Derechos", "derechos"), ]$term2 <- "Derecho"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("Derecha", "Derechas", "derecha", "derechas"), ]$term1 <- "Derecha"
cooc_event3[cooc_event3$term2 %in% c("Derecha", "Derechas", "derecha", "derechas"), ]$term2 <- "Derecha"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("#Apruebo", "Apruebo", "#apruebo", "apruebo"), ]$term1 <- "Apruebo"
cooc_event3[cooc_event3$term2 %in% c("#Apruebo", "Apruebo", "#apruebo", "apruebo"), ]$term2 <- "Apruebo"
# ---------------- #
cooc_event3[cooc_event3$term1 %in% c("AsambleaConstiyente", "#AsambleaConstiyente", "#AsambleaConstituyente", "#AsambleaConstituyente", "asambleaconstituyente", "#asambleaconstituyente"), ]$term1 <- "AsambleaConstiyente"
cooc_event3[cooc_event3$term2 %in% c("AsambleaConstiyente", "#AsambleaConstiyente", "#AsambleaConstituyente", "#AsambleaConstituyente", "asambleaconstituyente", "#asambleaconstituyente"), ]$term2 <- "AsambleaConstiyente"
```

## Agenda

- Key Dates in the Social Movement of Chilean Mobilizations

- Constructing a Co-occurrence Network Based on the Word 'Democracy' in a Text Corpus 

- Merging Text

- Visualizing Co-occurrence Frequency with Network Analysis


## Key dates for Chilean Mobilizations

- Missing:  _18 Oct 2019 (17 Oct 12:00 - 19 Oct 12:00)_

- Completed: ___Event 1:___ _2019-10-26, 2019-10-27 (n = 81655)_,  ___Event 2:___ _2019-11-14, 2019-11-15, 2019-11-16 (n = 198853)_, ___Event 3___ _2020-10-24, 2020-10-25, 2020-10-26 ( n = 143320)_, ___Event 4:___ _2021-05-14, 2021-05-15, 2021-05-16 ( n = 13207)_, ___Event 5:___ _2022-09-03, 2022-09-04, 2022-09-05 ( n = 172130)_



## Words Related to __“Democracy”__ Starting with Democ***

- Word Selection: democracia, demócrata, demócratas, democrática,democráticas, democrático, democráticos, 
democráticamente, democratización, democratizaciones, democratizador, democratizadora,
democratizar, democratizada, democratizadas, democratizado, and democratizados.

- Removal Stopword: ---

## Merging Synonyms

- [rechazo, r3ch4z0],  [pais, país], [histó, historico, histórico], [chilenos, chilenas, chilen@s], [sera, será], [subsidiario, subsidiaria, subsidiariedad], [participativo, participativa]

- [água, agua], [nuevo, nueva], [demócrata,  demócratas], [democrática, democráticas, democrático, democráticos], [democratización, democratizaciones]

##

- [democratizador,  democratizadora], [democratizada,  democratizadas, democratizado, democratizados], [Derecho, derecho, Derechos,  derechos]

- [Derecha, Derechas, derecha, derechas], [#Apruebo,  Apruebo,  #apruebo, apruebo], [AsambleaConstiyente, #AsambleaConstiyente, AsambleaConstituyente, #AsambleaConstituyente, asambleaconstituyente, #asambleaconstituyente]
 
## Reformated Twittre Dataframe


```{r}
#| include: false
load("../deminova-data/tweets_chile_event1.RData")
```



```{r  fig.width=3, fig.height=4}
#| include: true
options(scipen = 99999)
tweets_chile_event1|>
  head(n=3) |>
  kbl() |>
  kable_styling(font_size = 18)
```

 
## Tokenization in Pre-trained Model

```{r}
#| include: false
load("../deminova-data/tokened_event1.RData")
```



```{r  fig.width=3, fig.height=4}
#| include: true
options(scipen = 99999)
tokened_event1|>
  head(n=3) |>
  kbl() |>
  kable_styling(font_size = 16)
```


## Visualizing Co-occurrence Frequency with Network Analysis

- Top 30

- Comparison:  _Top 20 at frequency_ and _Top 30 at Co-occurrenceplot_

- Dates: _18 Oct 2019_, _25 Oct 2019_ and _15 Nov 2019_


# Event 1: ___18 Oct 2019___

- Dataframe: Top 20 Co-occurrence

- Co-occurrence Network: ___18 Oct 2019 Between 1 and 200___

## 18 Oct 2019 Top 20
```{r}
cooc_event1[1:10,] |>
  head(n=20) |>
  kbl() |>
  kable_styling(font_size = 16)
```


## 18 Oct 2019 Between Top 1 and 30
```{r}
cooc_event1[1:30,] |>
  igraph::graph_from_data_frame() |>
  ggraph::ggraph( layout = "kk") +
  ggraph::geom_edge_link(aes(width = `Co-Occurrence Windows`,edge_alpha = `Co-Occurrence Windows`), 
                         edge_colour = edge_colour_set[[4]],  alpha = 0.2) +
  # ggraph::geom_node_point(size = 15, shape =15, color = color_palette_set[[2]] , alpha = 0.8) +
  # ggraph::geom_node_point(size = 19, shape =22, color = "black") +
  ggraph::geom_node_text(aes(label = name), 
                         size = 4, 
                         repel = TRUE,
                         col = edge_colour_set[[3]], fontface = "bold") +
  ggraph::theme_graph(base_family = "Arial Narrow") +
  ggplot2::labs(title = "", subtitle = "") +
  ggplot2::theme_void() +
  ggplot2::theme(legend.key.size = unit(4.5, "cm"),  
                 legend.key.height = unit(4.5, "cm"),  
                 legend.key.width = unit(4.5, "cm"),  
                 legend.title = element_text(size=10), 
                 legend.text = element_text(size=22)) +
  guides(shape = guide_legend(override.aes = list(size = 1))) +
  theme(legend.title = element_text(size = 15), 
        legend.text = element_text(size = 8)) +  
  ggtitle("18 Oct 2019 between 1 and 30") +
  theme(plot.title = element_text(size = 20, face = "bold", hjust = 0.5, vjust = 0.5))


```


# Event 2: 25 Oct 2019

- Dataframe: Top 20 Co-occurrence

- Co-occurrence Network: ___25 Oct 2019 Between 1 and 30___

## 25 Oct 2019 Top 20
```{r}
cooc_event2[1:200,] |>
  head(n=20) |>
  kbl() |>
  kable_styling(font_size = 16)
```

## 25 Oct 2019 between 1 and 30
```{r}
cooc_event2[1:30,] |>
  igraph::graph_from_data_frame() |>
  ggraph::ggraph( layout = "kk") +
  ggraph::geom_edge_link(aes(width = `Co-Occurrence Windows`,edge_alpha = `Co-Occurrence Windows`), 
                         edge_colour = edge_colour_set[[2]]) +
  # ggraph::geom_node_point(size = 15, shape =15, color = color_palette_set[[2]] , alpha = 0.8) +
  # ggraph::geom_node_point(size = 19, shape =22, color = "black") +
  ggraph::geom_node_text(aes(label = name), 
                         size = 4, 
                         repel = TRUE,
                         col = edge_colour_set[[3]], fontface = "bold") +
  ggraph::theme_graph(base_family = "Arial Narrow") +
  ggplot2::labs(title = "", subtitle = "") +
  ggplot2::theme_void() +
  ggplot2::theme(legend.key.size = unit(4.5, "cm"),  
                 legend.key.height = unit(4.5, "cm"),  
                 legend.key.width = unit(4.5, "cm"),  
                 legend.title = element_text(size=10), 
                 legend.text = element_text(size=22)) +
  guides(shape = guide_legend(override.aes = list(size = 1))) +
  theme(legend.title = element_text(size = 15), 
        legend.text = element_text(size = 8)) +  
  ggtitle("25 Oct 2019 between 1 and 30") +
  theme(plot.title = element_text(size = 20, face = "bold", hjust = 0.5, vjust = 0.5))
```


# Event 3: 15 Nov 2019

- Dataframe: Top 20 Co-occurrence

- Co-occurrence Network: ___15 Nov 2019 Between 1 and 30___

## 15 Nov 2019 Top 20
```{r}
cooc_event3[1:200,] |>
  head(n=20) |>
  kbl() |>
  kable_styling(font_size = 16)
```

## 15 Nov 2019 between 1 and 30
```{r}
cooc_event3[1:30,] |>
  igraph::graph_from_data_frame() |>
  ggraph::ggraph( layout = "kk") +
  ggraph::geom_edge_link(aes(width = `Co-Occurrence Windows`,edge_alpha = `Co-Occurrence Windows`), 
                         edge_colour = edge_colour_set[[2]]) +
  # ggraph::geom_node_point(size = 15, shape =15, color = color_palette_set[[2]] , alpha = 0.8) +
  # ggraph::geom_node_point(size = 19, shape =22, color = "black") +
  ggraph::geom_node_text(aes(label = name), 
                         size = 4, 
                         repel = TRUE,
                         col = edge_colour_set[[3]], fontface = "bold") +
  ggraph::theme_graph(base_family = "Arial Narrow") +
  ggplot2::labs(title = "", subtitle = "") +
  ggplot2::theme_void() +
  ggplot2::theme(legend.key.size = unit(4.5, "cm"),  
                 legend.key.height = unit(4.5, "cm"),  
                 legend.key.width = unit(4.5, "cm"),  
                 legend.title = element_text(size=10), 
                 legend.text = element_text(size=22)) +
  guides(shape = guide_legend(override.aes = list(size = 1))) +
  theme(legend.title = element_text(size = 15), 
        legend.text = element_text(size = 8)) +  
  ggtitle("15 Nov 2019 between 1 and 30") +
  theme(plot.title = element_text(size = 20, face = "bold", hjust = 0.5, vjust = 0.5))
```

